---
title: "CSX415_Project_flight_delay_cancellation_analysis"
author: "Ajey Patil"
date: "5/7/2018"
output: html_document
---

## R Markdown
### Data Cleaning done in load.project() data munging

```{r, message=F, warning=F}
#currdir <- getwd()
#install.packages('ProjectTemplate')
library(ProjectTemplate)
load.project()
```

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo=TRUE)
```

## Install Packages

```{r install packages}
#Example package for RMSE calculation in Regression Analysis
#devtools::install_github("ajeypatil/rmse")
#library(rmse)
```

## Perform Exploratory Data Analysis
#### graphs stored in graph directory

```{r Perform Exploratory Data Analysis : graphs stored in graph directory}
source('src/01-EDA/CSX415_Project_ExploratoryDataAnalysis.R')
```
## PreProcess Data
#### Remove zero variance columns
#### Test-Train split
```{r preprocess}
source('src/02-PREPROCESS/CSX415_Project_process.R')
```

## Modelling
#### Apply Model

### Naive Bayes
```{r naive bayes}
source('src/03-MODELS/CSX415_Project_Data_Model_Naive.R')
#nb.model
#summary(nb.model)
plot(nb.model)
```

### Logistic Regression model
```{r glm}       
# Logistic Regression model for flights data takes more than 10 hours
# to train, the trained model is saved but is 3.9 Gb in size (.rds)
# Also the ROC calculated is only 0.592, hence not using this model
#source('src/03-MODELS/CSX415_Project_Data_Model_LogisticRegression.R')
#glm.model
#summary(glm.model)
#plot.roc(TestData$DelayedOrCancelled,glm_predictions,print.auc=TRUE,main="GLM Model ROC")
```

### Tree
```{r rpart}       
source('src/03-MODELS/CSX415_Project_Data_Model_Tree.R')
#tree.model
#summary(tree.model)
#plot(tree.model)
plot.roc(TestData$DelayedOrCancelled,tr_predictions[,2],print.auc=TRUE,main="Tree Model ROC")
```

## Model Evaluation
### Naive Bayes Model Evaluation

```{r model Naive Bayes evaluation}
confusionMatrix(TestData$DelayedOrCancelled,nb_predictions)
```


### Tree Model Evaluation

```{r Tree Model evaluation}
tr_pred <- ifelse((tr_predictions[,2]>0.8), 1,0)
confusionMatrix(TestData$DelayedOrCancelled,tr_pred)
```

## Model Selection
### Tree Model is more accurate and ROC is greater than 0.75 as required
### compared to Naive Bayes model.
### .
### Logistic Regression model takes long time to train and ROC is less
### than 0.65 hence not selecting Logistic Regression model also because
### saved model .rds is 3.9 Gb in size hence not suitable for deloyment
### .
### Comparing the metrics, the accuracy and Kappa values of Tree Model
### are greater than Naive Bayes Model
### .
### Conclusion: Tree Model satisfies the requirements criteria of 
### accuracy greater than 70% and ROC(AUC) greater than 0.65 and hence
### used for deployment

